\plaintitle

### 2016-09-21 drafts/labor/trackingWork.tex
renamed research_implications.tex to discussion.tex
added a conclusion.tex file. finished with discussion (i think)
maybe i should also let the trackingWork PDF finish compiling
conclusion

% Make sure hyperref comes last of your loaded packages, to give it a
% fighting chance of not being over-written, since its job is to
% redefine many LaTeX commands.
\definecolor{linkColor}{RGB}{6,125,233}
\hypersetup{%
  pdftitle={\plaintitle},
% Use \plainauthor for final version.
%  pdfauthor={\plainauthor},
  pdfauthor={\emptyauthor},
  pdfkeywords={\plainkeywords},
  bookmarksnumbered,
  pdfstartview={FitH},
  colorlinks,
  citecolor=blue, % black,
  filecolor=blue, % black,
  linkcolor=blue, % black,
  urlcolor=linkColor,
  breaklinks=true,
  hypertexnames=false
}

@@

\DTMsetdatestyle{mmddyyyy}
\DTMsetup{datesep=/}
\pagestyle{fancy}
\lfoot{Last compiled \today~at \DTMcurrenttime}
\cfoot{}
\rfoot{page \thepage/\pageref*{LastPage}}
\fancyhead{}
\pagenumbering{arabic}
\renewcommand{\headrulewidth}{0pt}

@@

\renewcommand{\footnotesize}{\normalsize} % i don't need small text! (no but really remove this before submitting)
\begin{document}
\renewcommand{\topic}[1]{#1} % don't do anything with \topic sentences; this is just for drafting 
\renewcommand{\joke}[1]{} % don't do anything with \jokes! Just throw them away! (Better to drop it than accidentally include it)
\renewcommand{\onlyinsubfile}[1]{}
\renewcommand{\notinsubfile}[1]{#1}
\renewcommand{\note}[1]{\onlyinsubfile{\note{#1}}}

@@

\keywords{\plainkeywords}
\subfile{introduction.tex}
\subfile{piecework_lit.tex}
\subfile{cases.tex}
\subfile{research_implications.tex}

@@

  % \section{Conclusion}
  % \citeauthor{crowdworkFuture} discussed many of the challenges and problems in crowd work in \citeyear{crowdworkFuture},
  % but didn't necessarily situate the notion of crowd work in a broader context.
  % This paper attempts to fill that gap, and in doing so hopes
  % to give the research community theoretical grounding to work with and within on--demand labor more successfully.
  % But more than that, we hope to have addressed important questions to inform how we actually might make crowd work
  % a career in which we want our children to work.
}
\theendnotes

>>>>

% Make sure hyperref comes last of your loaded packages, to give it a
% fighting chance of not being over-written, since its job is to
% redefine many LaTeX commands.
\definecolor{linkColor}{RGB}{6,125,233}
\hypersetup{%
  pdftitle={\plaintitle},
% Use \plainauthor for final version.
%  pdfauthor={\plainauthor},
  pdfauthor={\emptyauthor},
  pdfkeywords={\plainkeywords},
  bookmarksnumbered,
  pdfstartview={FitH},
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=black,
  urlcolor=linkColor,
  breaklinks=true,
  hypertexnames=false
}

@@

% \DTMsetdatestyle{mmddyyyy}
% \DTMsetup{datesep=/}
% \pagestyle{fancy}
% \lfoot{Last compiled \today~at \DTMcurrenttime}
% \cfoot{}
% \rfoot{page \thepage/\pageref*{LastPage}}
% \fancyhead{}
% \pagenumbering{arabic}
\renewcommand{\headrulewidth}{0pt}

@@

\renewcommand{\topic}[1]{#1} % don't do anything with \topic sentences; this is just for drafting 
\renewcommand{\footnotesize}{\normalsize} % i don't need small text! (no but really remove this before submitting)
\begin{document}
\renewcommand{\topic}[1]{#1} % don't do anything with \topic sentences; this is just for drafting 
\renewcommand{\joke}[1]{} % don't do anything with \jokes! Just throw them away! (Better to drop it than accidentally include it)
\renewcommand{\onlyinsubfile}[1]{}
\renewcommand{\notinsubfile}[1]{#1}
\renewcommand{\note}[1]{\onlyinsubfile{\note{#1}}}

@@

\keywords{\plainkeywords}
\subfile{introduction.tex}
\subfile{piecework_lit.tex}
\subfile{cases.tex}
\subfile{discussion.tex}
\subfile{conclusion.tex}

@@

  % \section{Conclusion}
  % \citeauthor{crowdworkFuture} discussed many of the challenges and problems in crowd work in \citeyear{crowdworkFuture},
  % but didn't necessarily situate the notion of crowd work in a broader context.
  % This paper attempts to fill that gap, and in doing so hopes
  % to give the research community theoretical grounding to work with and within on--demand labor more successfully.
  % But more than that, we hope to have addressed important questions to inform how we actually might make crowd work
  % a career in which we want our children to work.
}
% \theendnotes
